Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.Rmd
revised figure placement, and captions for figs 14, 15

<!--
```{r example-poly-lineup, fig.height=5, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup[["poly_24"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```
-->

@@

@@

<!--
```{r example-heter-lineup, fig.height = 5, fig.cap="Lineup heter-169 in experiment II. Can you spot the most different plot? \\label{fig:example-heter-lineup}"}

@@

VI_MODEL$plot_lineup(vi_lineup$heter_471$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```
-->

@@

```{r poly-example, fig.height = 5, fig.cap = "Lineup poly-270 with $log_e(E) = 3.89$ produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern."}
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r heter-example, fig.height = 5, fig.cap = 'Lineup heter-331 with $log_e(E) = 4.02$ produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.'}
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

>>>>

@@

```{r example-poly-lineup, fig.height=7, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup[["poly_24"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r example-heter-lineup, fig.height = 7, fig.cap="Lineup heter-169 in experiment II. Can you spot the most different plot? \\label{fig:example-heter-lineup}"}

@@

VI_MODEL$plot_lineup(vi_lineup$heter_471$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r poly-example, fig.height = 7, fig.cap = "Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern. It has effect size $= 3.89$. Interestingly, all the lineups in this group are higher order polynomials (M, Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!"}
# plot poly-270 
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r heter-example, fig.height = 7, fig.cap = 'The single heteroskedasticity lineup that is rejected by the visual test but not by the BP test. The data plot at panel 17 contains a "Butterfly" shape. It has effect size$ = 4.02$. It is a mystery as to why this is not detected by the BP test.'}
# plot heter-331
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.tex
revised figure placement, and captions for figs 14, 15

@@

@@

\caption{Lineup poly-270 with $log_e(E) = 3.89$ produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern.}\label{fig:poly-example}
\end{figure}

@@

\caption{Lineup heter-331 with $log_e(E) = 4.02$ produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.}\label{fig:heter-example}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/example-poly-lineup-1}

\caption{Lineup poly-24 in experiment I. Can you spot the most different plot? \label{fig:example-poly-lineup}}\label{fig:example-poly-lineup}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/example-heter-lineup-1}

\caption{Lineup heter-169 in experiment II. Can you spot the most different plot? \label{fig:example-heter-lineup}}\label{fig:example-heter-lineup}
\end{figure}

@@

\caption{Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern. It has effect size $= 3.89$. Interestingly, all the lineups in this group are higher order polynomials (M, Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!}\label{fig:poly-example}
\end{figure}

@@

\caption{The single heteroskedasticity lineup that is rejected by the visual test but not by the BP test. The data plot at panel 17 contains a "Butterfly" shape. It has effect size$ = 4.02$. It is a mystery as to why this is not detected by the BP test.}\label{fig:heter-example}
\end{figure}
